A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Minor fix

  \subsubsection{Miscellaneous} \eval is also used in R packages to get around
  various limitations. For example, in \datatable package, \eval is used to modify
  a binding in the \base package of R. Bindings in the \base package are locked
  for modification and require explicit unlocking using \unlockBinding function.
  However using this function directly triggers a warning during package building
  process which statically analyzes the package for use of such restricted
  functions. The \datatable gets around this limitation by enclosing the call to
  \unlockBinding inside \eval.

>>>>

  \subsubsection{Miscellaneous} \eval is also used in R packages to get around
  various limitations. For example, in \datatable package, \eval is used to modify
  a binding in the \base package of R. Bindings in the \base package are locked
  for modification and require explicit unlocking using \unlockBinding function.
  However, directly using this function triggers a warning during package building
  process which statically analyzes the package for use of such restricted
  functions. The \datatable gets around this limitation by enclosing the call to
  \unlockBinding inside \eval.
